A Privacy Aware Mobile Sensor Application

### 2015-06-11 paper.tex
- minor changins

\begin{figure}
\newcommand{\tcell}[1]{\parbox[c][2cm]{4cm}{\vspace{3mm}#1\vspace{3mm}}}
\newcommand{\thead}[1]{\tcell{\Large\centering\textbf{#1}}}
\newcommand{\tbody}[1]{\tcell{\Large\centering #1}}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
& \thead{Privacy of the Person}
& \thead{Privacy of Behaviour and Action}
& \thead{Privacy of Communication}
& \thead{Privacy of Data and Image}
& \thead{Privacy of Thoughts and Feelings}
& \thead{Privacy of Location and Space}
& \thead{Privacy of Association}
\\\hline\hline
\thead{GPS Sensor}
& \tbody{0.5} % Privacy of the Person
& \tbody{0.5} % Privacy of Behaviour and Action
& \tbody{0} % Privacy of Communication
& \tbody{1} % Privacy of Data and Image
& \tbody{0} % Privacy of Thoughts and Feelings
& \tbody{1} % Privacy of Location and Space
& \tbody{0.5} % Privacy of Association
\\\hline
\thead{Motion Sensors}
& \tbody{1} % Privacy of the Person
& \tbody{0.5} % Privacy of Behaviour and Action
& \tbody{0} % Privacy of Communication
& \tbody{1} % Privacy of Data and Image
& \tbody{0} % Privacy of Thoughts and Feelings
& \tbody{0} % Privacy of Location and Space
& \tbody{0} % Privacy of Association
\\\hline
\thead{Networking Sensors}
& \tbody{0.5} % Pricacy of the Person
& \tbody{0.5} % Pricacy of Behaviour and Action
& \tbody{0} % Pricacy of Communication
& \tbody{1} % Pricacy of Data and Image
& \tbody{0} % Pricacy of Thoughts and Feelings
& \tbody{1} % Pricacy of Location and Space
& \tbody{1} % Pricacy of Association
\\\hline
%\thead{HAR}
%& \tbody{-} % Pricacy of the Person
%& \tbody{-} % Pricacy of Behaviour and Action
%& \tbody{-} % Pricacy of Communication
%& \tbody{-} % Pricacy of Data and Image
%& \tbody{-} % Pricacy of Thoughts and Feelings
%& \tbody{-} % Pricacy of Location and Space
%& \tbody{-} % Pricacy of Association
%\\\hline
%\thead{SLD}
%& \tbody{-} % Pricacy of the Person
%& \tbody{-} % Pricacy of Behaviour and Action
%& \tbody{-} % Pricacy of Communication
%& \tbody{-} % Pricacy of Data and Image
%& \tbody{-} % Pricacy of Thoughts and Feelings
%& \tbody{-} % Pricacy of Location and Space
%& \tbody{-} % Pricacy of Association
%\\\hline
\end{tabular}
}
\newline
\newline
{\scriptsize 
0: No Impact,
0.5: Indirect Impact,
1: Direct Impact}
\caption{Sensor Data Privacy Impact Matrix}
\label{figure:Sensor Data Privacy Impact Matrix}
\end{figure}

@@

\subsubsection{Conflicts of Interests}
\label{subsubsection:Conflicts of Interests}
Different actors have different interests which can be in conflict with each other. This section outlines the Conflicts of Interests between the actors of the proposed IT system architecture. The emphasis here is to put on prominent existing conflicts, because they provide a foundation for vulnerabilities and subsequent threats.

@@

\textbf{Risk of T5/6. Information Leak and Social Engineering.} In our scenario we assume that the culture and ethics inside the
service provider company and travel agencies are very high, so that
the information leak scenario has a likeliness of $1$ (Low). The harm of such an information leaked is $3$ High, so that the
resulting risk is calculated as $4$.

>>>>

\begin{figure}
\newcommand{\tcell}[1]{\parbox[c][2cm]{4cm}{\vspace{3mm}#1\vspace{3mm}}}
\newcommand{\thead}[1]{\tcell{\Large\centering\textbf{#1}}}
\newcommand{\tbody}[1]{\tcell{\Large\centering #1}}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
& \thead{Privacy of the Person}
& \thead{Privacy of Behaviour and Action}
& \thead{Privacy of Communication}
& \thead{Privacy of Data and Image}
& \thead{Privacy of Thoughts and Feelings}
& \thead{Privacy of Location and Space}
& \thead{Privacy of Association}
\\\hline\hline
\thead{GPS Sensor}
& \tbody{0.5} % Privacy of the Person
& \tbody{0.5} % Privacy of Behaviour and Action
& \tbody{0} % Privacy of Communication
& \tbody{1} % Privacy of Data and Image
& \tbody{0.5} % Privacy of Thoughts and Feelings
& \tbody{1} % Privacy of Location and Space
& \tbody{0.5} % Privacy of Association
\\\hline
\thead{Motion Sensors}
& \tbody{1} % Privacy of the Person
& \tbody{0.5} % Privacy of Behaviour and Action
& \tbody{0} % Privacy of Communication
& \tbody{1} % Privacy of Data and Image
& \tbody{0} % Privacy of Thoughts and Feelings
& \tbody{0} % Privacy of Location and Space
& \tbody{0} % Privacy of Association
\\\hline
\thead{Networking Sensors}
& \tbody{0.5} % Pricacy of the Person
& \tbody{0.5} % Pricacy of Behaviour and Action
& \tbody{0} % Pricacy of Communication
& \tbody{1} % Pricacy of Data and Image
& \tbody{0.5} % Pricacy of Thoughts and Feelings
& \tbody{1} % Pricacy of Location and Space
& \tbody{1} % Pricacy of Association
\\\hline
%\thead{HAR}
%& \tbody{-} % Pricacy of the Person
%& \tbody{-} % Pricacy of Behaviour and Action
%& \tbody{-} % Pricacy of Communication
%& \tbody{-} % Pricacy of Data and Image
%& \tbody{-} % Pricacy of Thoughts and Feelings
%& \tbody{-} % Pricacy of Location and Space
%& \tbody{-} % Pricacy of Association
%\\\hline
%\thead{SLD}
%& \tbody{-} % Pricacy of the Person
%& \tbody{-} % Pricacy of Behaviour and Action
%& \tbody{-} % Pricacy of Communication
%& \tbody{-} % Pricacy of Data and Image
%& \tbody{-} % Pricacy of Thoughts and Feelings
%& \tbody{-} % Pricacy of Location and Space
%& \tbody{-} % Pricacy of Association
%\\\hline
\end{tabular}
}
\newline
\newline
{\scriptsize 
0: No Impact,
0.5: Indirect Impact,
1: Direct Impact}
\caption{Sensor Data Privacy Impact Matrix}
\label{figure:Sensor Data Privacy Impact Matrix}
\end{figure}

@@

\subsubsection{Conflicts of Interests}
\label{subsubsection:Conflicts of Interests}
Different actors have different interests which can be in conflict with each other. This section outlines the Conflicts of Interests between the actors of the proposed IT system architecture. The emphasis here is to put on prominent existing conflicts, because they provide a foundation for vulnerabilities and subsequent threats. A profit-driven conflict between the Service Provider and the privacy of citizens has been omitted for the sake of clarity.

@@

\textbf{Risk of T5/6. Information Leak and Social Engineering.} In our scenario we assume that the culture and ethics of the employees inside the
service provider company and travel agencies are very high, so that
the information leak scenario has a likeliness of $1$ (Low). The harm of such an information leaked is $3$ High, so that the
resulting risk is calculated as $4$.
